Robustly decorrelating errors with mixed quantum gates

### 2020-01-21 decorrelation/mixed_unitaries.tex
one RB was in dolla signs
removing comments
updates before PRA

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% RevTeX 4.1 LaTeX
% Kevin C. Young
% Scalable & Secure Systems Research (08961)
% Thu Mar  5 15:29:19 PST 2015
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[aps,nofootinbib,pra,notitlepage,twocolumn]{revtex4-1}
\usepackage{amsfonts,amsmath,amssymb,amsthm}
 \usepackage{array,bm,color}
\usepackage{epsfig,graphicx,nomencl,revsymb4-1,upgreek,url}
\usepackage{hyperref}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{calc}
\usepackage{siunitx}
\usepackage{tabularx}
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\graphicspath{{./figures/}}
\hypersetup{colorlinks=true, pdfauthor=Anthony M. Polloreno, pdftitle=Robustly decorrelating errors with mixed quantum gates, citecolor=blue, linkcolor=blue}
\newcommand{\tr}{{\rm Tr\thinspace}}
\newcommand{\bra}[1]{\ensuremath{\left\langle{#1}\right\vert}}
\newcommand{\ket}[1]{\ensuremath{\left\vert{#1}\right\rangle}}
\newcommand{\braket}[2]{\left\langle #1 | #2 \right\rangle}
\newcommand{\ketbra}[2]{\left| #1 \right\rangle\!\!\!\,\left\langle #2 \right|}
\newcommand{\abs}[1]{\left\vert #1 \right\vert}
\newcommand{\expect}[1]{\ensuremath{\left\langle{#1}\right\rangle}}
\newcommand{\timeorder}{\ensuremath{\underset{\leftarrow}{\mathcal{T}}}}
% \newcommand{\identmat}{{\mathbb1}}
\newcommand{\order}[1]{\mathcal{O}\left( #1 \right)}
\newcommand{\diag}[1]{\mathrm{diag}\{#1\}}
\newcommand{\trans}[1]{#1^\mathsf{T}}
\newcommand{\T}{\mathsf{T}}
\newcommand{\erf}[1]{Eq.~(\ref{#1})}
\newcommand{\needcite}{{\color{blue}\textsuperscript{[citation needed]}}}
% \newcommand{\note}[1]{{\color{red}[#1]}}
\newcommand{\note}[1]{}
\newcommand{\kcy}[1]{{\color{red}[#1]\textsubscript{\rm{KCY}}}}
\newcommand{\amp}[1]{{\color{red}[#1]\textsubscript{\rm{AMP}}}}
\newcommand{\deriv}[0]{{\frac{d}{d\vec{\delta}}}}

@@

\begin{abstract}
\noindent Coherent errors in quantum operations are ubiquitous. Whether arising from spurious environmental couplings or errors in control fields, such errors can accumulate rapidly and degrade the performance of a quantum circuit significantly more than an average gate fidelity may indicate. As Hastings \cite{Hastings2017} and Campbell \cite{Campbell2017} have recently shown, by replacing the deterministic implementation of a quantum gate with a randomized ensemble of implementations, on can dramatically suppress coherent errors. Our work begins by reformulating the results of Hastings and Campbell as a quantum optimal control problem. We then discuss a family of convex programs designed to improve the performance, implementability, and robustness of the resulting mixed quantum gates. Finally, we implement these mixed quantum gates on a superconducting qubit and discuss randomized benchmarking results consistent with a marked reduction in the coherent error.\\
{[1]} M. B. Hastings, \emph{Quantum Information \& Computation} 17, 488 (2017). \\
{[2]} E. Campbell, \emph{Physical Review A} 95, 042306 (2017).
\end{abstract}

@@

Campbell \cite{Campbell2017,1811.08017} and Hastings \cite{Hastings2017} have developed a technique for suppressing coherent noise by replacing deterministic gate implementations with a \emph{mixed quantum gate} (MQG) consisting of a randomly sampled ensemble of implementations. They focus on errors in gate compilation, such as those that arise from the Solovey-Kitaev algorithm, for which any lingering approximation errors are generally coherent, even if the underlying native gates are perfect. Different approximate gate compilations of the same target unitary will almost certainly result in different unitary errors. So by selecting from these various compilations at random, the resulting quantum channel becomes a mixture of unitaries \cite{DBLP:journals/corr/cs-CC-0012017}, which can have significantly less coherent error than any single compilation on its own. A very simple example of this reduction in coherent error by mixed quantum gates is illustrated in Fig.~\ref{fig:simple_example}.

Randomized protocols have a long history of outperforming their deterministic counterparts\cite{Viola2005, Santos2006}. In circuit models, Pauli Frame Randomization \cite{Wallman2016, 1803.01818} has been shown to reduce coherent errors by introducing randomness in a pre-compilation step. While Pauli Frame Randomization shares the some favorable properties with MQGs, we will see that MQGs additionally admit a hardware-efficient implementation and numerous useful modifications when they are posed as a numerical optimization problem.

@@

While generator-exact MQGs can provide a guaranteed suppression of the diamond distance, their effective error channels are unlikely to be a purely stochastic. Second- and higher-order terms in \eqref{eq:generators_and_effective_error} can easily contribute to lingering coherent errors that impact the efficient simulability of the channel. In order to definitively eliminate these coherent errors, we could instead seek weights, $\weight^P_i$, that annihilate the off-diagonal entries of the effective error map. The resulting diagonal error map will be Pauli-stochastic. For a single qubit gate, it takes the form,
% \begin{equation}
% 	\errmat_{eff} = 
% 	\left(\begin{array}{@{}ccccc@{}}
% 		\cdot & \cdot & \cdot & \cdot \\ 
%   		\cline{1-1}\cline{3-4}
%     	\multicolumn{1}{|c}{0} & \multicolumn{1}{|c}{\cdot} & \multicolumn{1}{|c}{0} & \multicolumn{1}{c|}{0} \\
%     	\cline{2-2}\cline{3-3}		
% 		\multicolumn{1}{|c}{0} & 0 & \multicolumn{1}{|c}{\cdot} & \multicolumn{1}{|c|}{0}\\
% 		\cline{3-3}\cline{4-4}	
% 		\multicolumn{1}{|c}{0} & 0 & 0 & \multicolumn{1}{|c}{\cdot}\\
% 		\cline{1-3}
% 	\end{array} 	
% 	\right).
% \end{equation}
\begin{equation}
	\errmat_{\rm{eff}} = \sum_i \weight_i^P \errmat_i = 
	\left(\begin{array}{@{}ccccc@{}}
		1 & 0 & 0 & 0 \\ 
    	0 &  p_x & 0 & 0 \\
		0 & 0 &  p_y & 0\\
		0 & 0 & 0 &  p_z\\
	\end{array} 	
	\right),
\end{equation}
where $p_x, p_y$ and $p_z$ are the rates of Pauli $X$, $Y$, and $Z$ errors, respectively. We refer to such channels as \emph{Pauli-exact} MQGs, and the same geometric argument we used in constructing generator-exact MQGs is again applicable here. The off-diagonal elements of the error map form a vector space, so we need only check that the origin is in the convex hull of the vectors of off-diagonal elements for each of the component operations, $\errmat_i$. If the error map contains non-unital components or correlated Pauli-stochastic errors (such as $X+Y$), then this strict geometric condition may not hold and no Pauli-exact MQG would exist. However, MQGs that approximate the Pauli-exact condition can be found via the convex programing techniques discussed in Sec.~\ref{sub:off_diagonals}.

% In the remainder of this paper, we will formalize this process, laying out efficient convex programs to both generate a family of unitary controls \kcy{do we do this?} and compute the weights required to yield either type of MQG. We discuss how one might include additional desiderata, including reduced sensitivity to environmental fluctuation as well as limiting the number of native unitaries that participate in the MQG.

% ==============================================================================
% Section: Constructing Useful mixed quantum gates
% ==============================================================================
\section{Constructing mixed quantum gates}
\label{sec:mixed_unitary_processes}
\noindent We now present a methodology for constructing mixed quantum channels, formalizing the intuitive approach discussed above with a series of explicit convex programs. As mentioned, our method requires two steps. The first is a control synthesis step, in which we construct an ensemble of gate implementations. Campbell and Hastings draw their ensembles from various different gate compilations, but for this work we use utilize quantum optimal control theory. Many standard control-generation algorithms, such as GRAPE \cite{Khaneja2005}, take a random initial guess for the control and iteratively improve it to yield a gate that well-approximates a target. By seeding such algorithms with many initial guesses, one can quickly construct a large ensemble of approximate quantum gates, each with a different error channel. We discuss this approach in some detail in Sec.~\ref{sec:numerical_results}.

@@

% In the examples that were discussed, all objective functions were linear, and reduced to finding a collection of controls whose convex hull contained the origin in some high-dimensional vector space. In those cases, the vectors might represent a collection of error generators or the off-diagonal elements of a collection of error maps. As we'll see in Section \ref{sub:adding_robustness}, we can also consider the derivatives of the error generators to minimize the sensitivity of the controls to drift. In this way, we see that by considering the appropriate collection of vectors, we can optimize our MQG for different purposes, and which routine we choose will depend on the quantities we are trying to minimize.

@@

%In both cases it is clear that we should select the gates with smaller error, i.e. $\{U_{\epsilon}, U_{-\epsilon}\}$, rather than those with larger error, to minimize the multiplicative coefficient on the error. Despite this, literature commonly assumes that all controls are less than some threshold value, below which differences in performance don't matter. \cite{Campbell2017} In realistic scenarios, some controls will have better performance than others, and it is important to select from those controls when able to. We will discuss numerical approaches to solving this Section \ref{sec:norm}.

%Another interesting property of the MQG given in Equation \ref{eq:balanced} is that it maintains its first-order insensitivity even in the presence of drift. In particular, if the control amplitudes that implement these gates drift, they will drift in equal and opposite ways. Thus, the resulting depolarizing channel (see Figure \ref{fig:simple_example}) will have a time-dependent strength, but it will remain first-order insensitivity to the static detuning $\epsilon$. In Section \ref{sec:robustly_mixed} we will provide a method for producing controls that exhibit this robustness to drift to arbitrary order. Given these considerations from this simple example, we will now consider a numerical strategy for generating MQGs.

% subsection first_order_generators (end)

% ==============================================================================
% Section: Off-diagonals
% ==============================================================================
% contrast coherent errors with stochastic where an expectation can be computed and then the circuit can be rerun, rather than having to track the the whole state.

@@

In particular, the well-known stabilizer formalism \cite{quant-ph/9807006} for quantum simluation gives a polynomial-time algorithm to compute expectation values of circuits consisting of only Clifford operations. These circuits are useful because they give examples of quantum circuits whose performance can be efficiently assessed using classical simulation. This has motivated significant development of these techniques, including extensions to simulating stabilizer circuits with mixed state inputs\cite{Aaronson2004} and linear combinations of stabilizer circuits. \cite{Yoder, Bennink2017} An interesting property of such simulation techniques is that the cost of the classical simulation is proportional to how non-Clifford the circuit is. Therefore Pauli-exact MQGs have a clear benefit - if the error channels of a circuit can be made to look more like Pauli-stochastic errors, they will be more amenable to efficient classical simulation.

Like generator-exact MQGs, the optimal weights can be found efficiently by a convex optimization. As above, we assume that we have access to $m$ distinct gate implementations, each of which is associated with its own error matrix, $\errmat_i$. We wish to construct an MQG whose effective error is Pauli-stochastic and is therefore diagonal. This can be done with the following simple minimization:
\begin{equation}\label{eq:minimization2}
  \begin{split}
    &\underset{\weight_i\geq0, \sum_i\weight_1=1}{\textbf{minimize}: } ||\sum_i\weight_i \errmat_i - \mathsf{diag}(\sum_i \weight_i \errmat_i)||_2\\
  \end{split}
\end{equation}
Here $(\mathsf{diag}(\mathcal{A}))_{ij} = \mathcal{A}_{ij}\delta_{ij}$ sets the off-diagonal elements of a matrix to zero. This can be more transparently written as a convex program by constructing the $(d^2-d)\times m$-dimensional matrix, $\mathbf{E}$, whose $i$\textsuperscript{th} column is a vector composed of all of the off-diagonal entries of the error generators $\errmat_i$. \footnote{Exactly \emph{how} the off-diagonal entries are vectorized is unimportant, so long as it is consistent across error matrices.} Eq.~\eqref{eq:minimization2} is then equivalent to 
\begin{equation}\label{eq:minimization3}
  \begin{split}
    &\underset{\weight_i\geq0, |\weight|_1=1}{\textbf{minimize}: } ||\mathbf{E}\cdot\vec\weight||_2
  \end{split}
\end{equation}
The similarity with Eq.~\ref{eq:minimization} is clear and the same methods can be used to solve both. If the solver routine finds a solution for which the cost function is equal to 0, then the resulting error channel will be \textit{exactly} a Pauli channel. 
%As mentioned, circuits composed of gates with Pauli stochastic error channels can be more efficiently simulated by Monte Carlo methods. Furthermore, if the bare circuit consists of only Clifford gates, stabilizer methods can be used in conjunction with the Monte Carlo methods to give sub-exponential simulation times.\cite{quant-ph/9807006} \kcy{Why this paper?}

@@

% ==============================================================================
% Section: Robustness
% ==============================================================================
\subsection{Secondary Objectives}
\noindent 
Often, the cost of generating distinct gate implementations is quite small, so large ensembles of them can be computed rather quickly. One may then have available many more distinct gate implementations than there are parameters in the relevant vector space (see Fig.~\ref{fig:vectorspace}). This can lead to the the minimization problems discussed in the previous section being massively under-constrained, yielding a large continuous family of exact solutions. Secondary objectives provide a means for choosing among this family of exact MQGs those with increased performance in a desired area. In this section we present explicit convex programs for such secondary objectives, including adding robustness to drift or model uncertainty, reducing the effective gate error, and minimizing the number of constituent gates utilized by the MQG. We choose to take generator-exact MQGs as our starting point, though the following sections apply equally well to Pauli-exact MQGs with only trivial modifications.

@@

% subsection adding_robustness (end)

@@

% then we can instead incentivize the construction of a lowest-error MQG by including an AGI penalty directly in the

% \begin{equation}\label{eq:minimization}
%   \begin{split}
%     &\underset{\weight_i\geq0, |\weight|_1=1}{\textbf{minimize}: } \sum_i \weight_i\; \AGI(\errmat_i)\\
%     & \textbf{subject to}: ||\mathbf{L}\cdot\vec\weight||_2 = 0 
%   \end{split}
% \end{equation}

% \begin{equation}\label{eq:minimization_l2}
% \begin{split}
% & \ \bunderbrace{\textbf{minimize}: }{\weight_i\geq0, |\weight|_1=1} ||{\mathbf{D}^{\ell}}\weight||_1+ \eta\sum\weight_i||D^0_i||_2\\
% &\ \ \textbf{subject to: } \forall n<\ell, ||\sum \weight_iD_i^n||=0\\
% \end{split}
% \end{equation}
% with $\eta \geq 0$. By increasing $\eta$, we can encourage the optimizer to include better controls while minimizing the diamond norm. The value of $\eta$ that is best for any particular problem instance will depend on the values in $\mathbf{D}^\ell$.

%Naively generating the 1Q 0MQG in the previous section results in nontrivial support on all the members of the control family. However, as we will see in the next section, we can rewrite the minimization to impose a sparsity constraint, and the resulting 0MQG uses just five of the controls. 
% ==============================================================================
% Section: Sparsity
% ==============================================================================

@@

\setlength{\tabcolsep}{0.5em} 
{\renewcommand{\arraystretch}{1.2}
% \newcolumntype{d}[1]{D{.}{.}{#1}}
\begin{table}[h]
	\centering
	\begin{tabular}{@{}ccc@{}}
		\hline
		Pulse name & Rotation error & RB error rate\\
		\hline
		$\mathsf{Pulse1}$ 	& 6.4\% 	& 1.1\% \\
		$\mathsf{Pulse2}$ 	& 3.9\% 	& 0.9\% \\
		$\mathsf{Pulse3}$ 	& --\,6.3\% 	& 1.1\% \\
		$\mathsf{Pulse4}$ 	& --\,8.8\% 	& 1.5\% \\
		Calibrated 			& $\cdot$  	& 0.7\% \\
		MQG 				& $\cdot$ 	& 0.8\% \\
		\hline
	\end{tabular}
	\caption{\textbf{Randomized benchmarking results:} The MQG outperforms all of the individual miscalibrated gates of which it is composed, achieving an RB number nearly as low as the carefully calibrated pulse. }
\label{tabl:rb}
\end{table}

By minimizing the off-diagonal elements of the process matrix, we expect the resulting MQG to display suppressed coherent error. To see that this is in fact the case, we can inspect the variance of the $RB$ survival probabilities for the MQG relative to the miscalibrated pulses. As discussed in \cite{Ball2016}, coherent errors will tend to broaden the distribution of RB survival probabilities over sequences at each length, generally manifesting as a long-tailed gamma distribution. Stochastic noise, such as depolarizing noise, will yield comparatively narrow, Gaussian-distributed success probabilities. In Fig.~\ref{fig:rb}, we plot the experimentally observed distribution of survival probabilities at sequence length $64$ for each of the benchmarked gate sets. We see that the intentionally miscalibrated controls in our RB experiment have long tails, consistent with coherent noise, while the calibrated and randomized implementations are both significantly less dispersed, consistent with stochastic errors. This experiment therefore provides compelling evidence that the MQG suffers considerably less coherent error than any of the miscalibrated gates from which it was constructed.

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=\columnwidth]{figures/1q_robustness_delta.pdf}
  \caption{\textbf{One-qubit robust generator-exact MQG} Numerical results showing the the diamond distance errors for a generator-exact MQG (dashed blue), a robust generator-exact MQG (solid orange), and a large set of bare unitary controls (thin solid grey) as a function of a the fractional amplitude error. The target is an $X_{\pi/2}$ gate on a single qubit. The generator-exact MQG dramatically outperforms both the robust generator-exact and any of the bare unitaries at $\delta=0$. However, even a relatively small amplitude error leads to a regime in which the the robust generator-exact will yield the better gate. Similar results are obtained for drift in the qubit frequency.}
  \label{fig:YMQG}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{figures/2q_robustness.pdf}
  \caption{\textbf{Two-qubit robust generator-exact MQG} Numerical results showing the the diamond distance errors for a generator-exact MQG (dashed blue), a robust generator-exact MQG (solid orange), and a large set of bare unitary controls (thin solid grey) as a function of a spurious detuning (quantified by the ratio of the detuning to the maximum control amplitude). It is intended to model a pair of qubits interacting via resonant exchange. Both MQGs can be seen to outperform the bare unitary control over a wide range of detunings. The robust generator-exact  MQG always outperforms the generator-exact MQG, and both MQGs outperform any of the bare unitary controls over a wide range of detunings. Similar results are obtained for drift in the qubit control amplitude.}
  \label{fig:2MQG}
\end{figure}

>>>>

\documentclass[aps,nofootinbib,pra,notitlepage,twocolumn]{revtex4-1}
\usepackage{amsfonts,amsmath,amssymb,amsthm}
 \usepackage{array,bm,color}
\usepackage{epsfig,graphicx,nomencl,revsymb4-1,upgreek,url}
\usepackage{hyperref}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{calc}
\usepackage{siunitx}
\usepackage{tabularx}
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\graphicspath{{./figures/}}
\hypersetup{colorlinks=true, pdfauthor=Anthony M. Polloreno, pdftitle=Robustly decorrelating errors with mixed quantum gates, citecolor=blue, linkcolor=blue}
\newcommand{\tr}{{\rm Tr\thinspace}}
\newcommand{\bra}[1]{\ensuremath{\left\langle{#1}\right\vert}}
\newcommand{\ket}[1]{\ensuremath{\left\vert{#1}\right\rangle}}
\newcommand{\braket}[2]{\left\langle #1 | #2 \right\rangle}
\newcommand{\ketbra}[2]{\left| #1 \right\rangle\!\!\!\,\left\langle #2 \right|}
\newcommand{\abs}[1]{\left\vert #1 \right\vert}
\newcommand{\expect}[1]{\ensuremath{\left\langle{#1}\right\rangle}}
\newcommand{\timeorder}{\ensuremath{\underset{\leftarrow}{\mathcal{T}}}}
\newcommand{\order}[1]{\mathcal{O}\left( #1 \right)}
\newcommand{\diag}[1]{\mathrm{diag}\{#1\}}
\newcommand{\trans}[1]{#1^\mathsf{T}}
\newcommand{\T}{\mathsf{T}}
\newcommand{\erf}[1]{Eq.~(\ref{#1})}
\newcommand{\needcite}{{\color{blue}\textsuperscript{[citation needed]}}}
\newcommand{\note}[1]{}
\newcommand{\kcy}[1]{{\color{red}[#1]\textsubscript{\rm{KCY}}}}
\newcommand{\amp}[1]{{\color{red}[#1]\textsubscript{\rm{AMP}}}}
\newcommand{\deriv}[0]{{\frac{d}{d\vec{\delta}}}}

@@

\begin{abstract}
\noindent Coherent errors in quantum operations are ubiquitous. Whether arising from spurious environmental couplings or errors in control fields, such errors can accumulate rapidly and degrade the performance of a quantum circuit significantly more than an average gate fidelity may indicate. As Hastings \cite{Hastings2017} and Campbell \cite{Campbell2017} have recently shown, by replacing the deterministic implementation of a quantum gate with a randomized ensemble of implementations, one can dramatically suppress coherent errors. Our work begins by reformulating the results of Hastings and Campbell as a quantum optimal control problem. We then discuss a family of convex programs designed to improve the performance, implementability, and robustness of the resulting mixed quantum gates. Finally, we implement these mixed quantum gates on a superconducting qubit and discuss randomized benchmarking results consistent with a marked reduction in the coherent error.\\
{[1]} M. B. Hastings, \emph{Quantum Information \& Computation} 17, 488 (2017). \\
{[2]} E. Campbell, \emph{Physical Review A} 95, 042306 (2017).
\end{abstract}

@@

Campbell \cite{Campbell2017,Campbell2019} and Hastings \cite{Hastings2017} have developed a technique for suppressing coherent noise by replacing deterministic gate implementations with a \emph{mixed quantum gate} (MQG) consisting of a randomly sampled ensemble of implementations. They focus on errors in gate compilation, such as those that arise from the Solovey-Kitaev algorithm, for which any lingering approximation errors are generally coherent, even if the underlying native gates are perfect. Different approximate gate compilations of the same target unitary will almost certainly result in different unitary errors. So by selecting from these various compilations at random, the resulting quantum channel becomes a mixture of unitaries \cite{DBLP:journals/corr/cs-CC-0012017}, which can have significantly less coherent error than any single compilation on its own. A very simple example of this reduction in coherent error by mixed quantum gates is illustrated in Fig.~\ref{fig:simple_example}.

Randomized protocols have a long history of outperforming their deterministic counterparts\cite{Viola2005, Santos2006}. In circuit models, Pauli Frame Randomization \cite{Wallman2016, 1803.01818, dahlen2018experimental} has been shown to reduce coherent errors by introducing randomness in a pre-compilation step. While Pauli Frame Randomization shares the some favorable properties with MQGs, we will see that MQGs additionally admit a hardware-efficient implementation and numerous useful modifications when they are posed as a numerical optimization problem.

@@

While generator-exact MQGs can provide a guaranteed suppression of the diamond distance, their effective error channels are unlikely to be purely stochastic. Second- and higher-order terms in \eqref{eq:generators_and_effective_error} can easily contribute to lingering coherent errors that impact the efficient simulability of the channel. In order to definitively eliminate these coherent errors, we could instead seek weights, $\weight^P_i$, that annihilate the off-diagonal entries of the effective error map. The resulting diagonal error map will be Pauli-stochastic. For a single qubit gate, it takes the form,

\begin{equation}
	\errmat_{\rm{eff}} = \sum_i \weight_i^P \errmat_i = 
	\left(\begin{array}{@{}ccccc@{}}
		1 & 0 & 0 & 0 \\ 
    	0 &  p_x & 0 & 0 \\
		0 & 0 &  p_y & 0\\
		0 & 0 & 0 &  p_z\\
	\end{array} 	
	\right),
\end{equation}
where $p_x, p_y$ and $p_z$ are the rates of Pauli $X$, $Y$, and $Z$ errors, respectively. We refer to such channels as \emph{Pauli-exact} MQGs, and the same geometric argument we used in constructing generator-exact MQGs is again applicable here. The off-diagonal elements of the error map form a vector space, so we need only check that the origin is in the convex hull of the vectors of off-diagonal elements for each of the component operations, $\errmat_i$. If the error map contains non-unital components or correlated Pauli-stochastic errors (such as $X+Y$), then this strict geometric condition may not hold and no Pauli-exact MQG would exist. However, MQGs that approximate the Pauli-exact condition can be found via the convex programing techniques discussed in Sec.~\ref{sub:off_diagonals}.

% ==============================================================================
% Section: Constructing Useful mixed quantum gates
% ==============================================================================
\section{Constructing mixed quantum gates}
\label{sec:mixed_unitary_processes}
\noindent We now present a methodology for constructing mixed quantum channels, formalizing the intuitive approach discussed above with a series of explicit convex programs. As mentioned, our method requires two steps. The first is a control synthesis step, in which we construct an ensemble of gate implementations. Campbell and Hastings draw their ensembles from various different gate compilations, but for this work we utilize quantum optimal control theory. Many standard control-generation algorithms, such as GRAPE \cite{Khaneja2005}, take a random initial guess for the control and iteratively improve it to yield a gate that well-approximates a target. By seeding such algorithms with many initial guesses, one can quickly construct a large ensemble of approximate quantum gates, each with a different error channel. We discuss this approach in some detail in Sec.~\ref{sec:numerical_results}.

@@

@@

@@

In particular, the well-known stabilizer formalism \cite{quant-ph/9807006} for quantum simluation gives a polynomial-time algorithm to compute expectation values of circuits consisting of only Clifford operations. These circuits are useful because they give examples of quantum circuits whose performance can be efficiently assessed using classical simulation. This has motivated significant development of these techniques, including extensions to simulating stabilizer circuits with mixed state inputs\cite{Aaronson2004} and linear combinations of stabilizer circuits\cite{Yoder, Bennink2017}. An interesting property of such simulation techniques is that the cost of the classical simulation is proportional to how non-Clifford the circuit is. Therefore Pauli-exact MQGs have a clear benefit - if the error channels of a circuit can be made to look more like Pauli-stochastic errors, they will be more amenable to efficient classical simulation.

Like generator-exact MQGs, the optimal weights can be found efficiently by a convex optimization. As above, we assume that we have access to $m$ distinct gate implementations, each of which is associated with its own error matrix, $\errmat_i$. We wish to construct an MQG whose effective error is Pauli-stochastic and is therefore diagonal. This can be done with the following simple minimization:
\begin{equation}\label{eq:minimization2}
  \begin{split}
    &\underset{\weight_i\geq0, \sum_i\weight_1=1}{\textbf{minimize}: } ||\sum_i\weight_i \errmat_i - \mathsf{diag}(\sum_i \weight_i \errmat_i)||_2\\
  \end{split}
\end{equation}
Here $(\mathsf{diag}(\mathcal{A}))_{ij} = \mathcal{A}_{ij}\delta_{ij}$ sets the off-diagonal elements of a matrix to zero. This can be more transparently written as a convex program by constructing the $(d^2-d)\times m$-dimensional matrix, $\mathbf{E}$, whose $i$\textsuperscript{th} column is a vector composed of all of the off-diagonal entries of the error generators $\errmat_i$. \footnote{Exactly \emph{how} the off-diagonal entries are vectorized is unimportant, so long as it is consistent across error matrices.} Eq.~\eqref{eq:minimization2} is then equivalent to 
\begin{equation}\label{eq:minimization3}
  \begin{split}
    &\underset{\weight_i\geq0, |\weight|_1=1}{\textbf{minimize}: } ||\mathbf{E}\cdot\vec\weight||_2
  \end{split}
\end{equation}
The similarity with Eq.~\ref{eq:minimization} is clear and the same methods can be used to solve both. If the solver routine finds a solution for which the cost function is equal to 0, then the resulting error channel will be \textit{exactly} a Pauli channel.

@@

% ==============================================================================
% Section: Robustness
% ==============================================================================
\subsection{Secondary Objectives}
\noindent 
Often, the cost of generating distinct gate implementations is quite small, so large ensembles of them can be computed rather quickly. One may then have available many more distinct gate implementations than there are parameters in the relevant vector space (see Fig.~\ref{fig:vectorspace}). This can lead to the minimization problems discussed in the previous section being massively under-constrained, yielding a large continuous family of exact solutions. Secondary objectives provide a means for choosing among this family of exact MQGs those with increased performance in a desired area. In this section we present explicit convex programs for such secondary objectives, including adding robustness to drift or model uncertainty, reducing the effective gate error, and minimizing the number of constituent gates utilized by the MQG. We choose to take generator-exact MQGs as our starting point, though the following sections apply equally well to Pauli-exact MQGs with only trivial modifications.

@@

@@

% ==============================================================================
% Section: Sparsity
% ==============================================================================

@@

\setlength{\tabcolsep}{0.5em} 
{\renewcommand{\arraystretch}{1.2}
\begin{table}[h]
	\centering
	\begin{tabular}{@{}ccc@{}}
		\hline
		Pulse name & Rotation error & RB error rate\\
		\hline
		$\mathsf{Pulse1}$ 	& 6.4\% 	& 1.1\% \\
		$\mathsf{Pulse2}$ 	& 3.9\% 	& 0.9\% \\
		$\mathsf{Pulse3}$ 	& --\,6.3\% 	& 1.1\% \\
		$\mathsf{Pulse4}$ 	& --\,8.8\% 	& 1.5\% \\
		Calibrated 			& $\cdot$  	& 0.7\% \\
		MQG 				& $\cdot$ 	& 0.8\% \\
		\hline
	\end{tabular}
	\caption{\textbf{Randomized benchmarking results:} The MQG outperforms all of the individual miscalibrated gates of which it is composed, achieving an RB number nearly as low as the carefully calibrated pulse. }
\label{tabl:rb}
\end{table}

By minimizing the off-diagonal elements of the process matrix, we expect the resulting MQG to display suppressed coherent error. To see that this is in fact the case, we can inspect the variance of the RB survival probabilities for the MQG relative to the miscalibrated pulses. As discussed in \cite{Ball2016}, coherent errors will tend to broaden the distribution of RB survival probabilities over sequences at each length, generally manifesting as a long-tailed gamma distribution. Stochastic noise, such as depolarizing noise, will yield comparatively narrow, Gaussian-distributed success probabilities. In Fig.~\ref{fig:rb}, we plot the experimentally observed distribution of survival probabilities at sequence length $64$ for each of the benchmarked gate sets. We see that the intentionally miscalibrated controls in our RB experiment have long tails, consistent with coherent noise, while the calibrated and randomized implementations are both significantly less dispersed, consistent with stochastic errors. This experiment therefore provides compelling evidence that the MQG suffers considerably less coherent error than any of the miscalibrated gates from which it was constructed.

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=\columnwidth]{1q_robustness_delta.pdf}
  \caption{\textbf{One-qubit robust generator-exact MQG} Numerical results showing the the diamond distance errors for a generator-exact MQG (dashed blue), a robust generator-exact MQG (solid orange), and a large set of bare unitary controls (thin solid grey) as a function of a the fractional amplitude error. The target is an $X_{\pi/2}$ gate on a single qubit. The generator-exact MQG dramatically outperforms both the robust generator-exact and any of the bare unitaries at $\delta=0$. However, even a relatively small amplitude error leads to a regime in which the the robust generator-exact will yield the better gate. Similar results are obtained for drift in the qubit frequency.}
  \label{fig:YMQG}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{2q_robustness.pdf}
  \caption{\textbf{Two-qubit robust generator-exact MQG} Numerical results showing the the diamond distance errors for a generator-exact MQG (dashed blue), a robust generator-exact MQG (solid orange), and a large set of bare unitary controls (thin solid grey) as a function of a spurious detuning (quantified by the ratio of the detuning to the maximum control amplitude). It is intended to model a pair of qubits interacting via resonant exchange. Both MQGs can be seen to outperform the bare unitary control over a wide range of detunings. The robust generator-exact  MQG always outperforms the generator-exact MQG, and both MQGs outperform any of the bare unitary controls over a wide range of detunings. Similar results are obtained for drift in the qubit control amplitude.}
  \label{fig:2MQG}
\end{figure}
